General constraints on magic distillation protocols from statistical mechanics

### 2021-05-28 magic_paper.tex
typos and punctuation

\begin{proof}
	The Lorenz curve of $\p$ relative to $\r$ passes through the origin $(r_{\pi(0)}, p_{\pi(0)}) := (0,0)$ and the points $(\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k p_{\pi(i)})$ where $\pi$ is the permutation that puts $p_i/r_i$ in non-increasing order.
	The function is continuous, and the slope of the curve away from the elbows is well-defined and takes the value 
\begin{equation}
	\frac{\sum_{i=0}^k p_{\pi(i)} - \sum_{i=0}^{k-1} p_{\pi(i)}}{\sum_{i=0}^k r_{\pi(i)} - \sum_{i=0}^{k-1} r_{\pi(i)}} = \frac{p_{\pi(k)}}{r_{\pi(k)}},
\end{equation}
with $k=0,1,2, \dots$ labeling the line-segments of the Lorenz curve in increasing order.
From the definition of the Lorenz curve, this implies the slope is piecewise constant, non-increasing on $[0,1]$ minus the elbow locations. Therefore, the Lorenz curve is a concave function on $[0,1]$. \ddd{[Not fully rigorous due to elbows... Here is an alternative proof:]}
\end{proof}
\begin{proof} Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and and $0$ otherwise. Also let $f_2(x)$ be equal to $L_{\p|\r}(x)$ on $[x_\star,1]$ and and $0$ otherwise. By inspection both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\p|\r}(x)$ for all $x\in [0,1]$. However the sum of two concave functions is also concave and so the result follows.
\end{proof}

>>>>

\begin{proof}
	The Lorenz curve of $\p$ relative to $\r$ passes through the origin $(r_{\pi(0)}, p_{\pi(0)}) := (0,0)$ and the points $(\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k p_{\pi(i)})$ where $\pi$ is the permutation that puts $p_i/r_i$ in non-increasing order.
	The function is continuous, and the slope of the curve away from the elbows is well-defined and takes the value 
\begin{equation}
	\frac{\sum_{i=0}^k p_{\pi(i)} - \sum_{i=0}^{k-1} p_{\pi(i)}}{\sum_{i=0}^k r_{\pi(i)} - \sum_{i=0}^{k-1} r_{\pi(i)}} = \frac{p_{\pi(k)}}{r_{\pi(k)}},
\end{equation}
with $k=0,1,2, \dots$ labeling the line-segments of the Lorenz curve in increasing order.
From the definition of the Lorenz curve, this implies the slope is piecewise constant, non-increasing on $[0,1]$ minus the elbow locations. Therefore, the Lorenz curve is a concave function on $[0,1]$. \ddd{[Not fully rigorous due to elbows... Here is an alternative proof:]}
\end{proof}
\begin{proof} Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and $0$ otherwise. Also let $f_2(x)$ be equal to $L_{\p|\r}(x)$ on $[x_\star,1]$ and $0$ otherwise. By inspection, both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\p|\r}(x)$ for all $x\in [0,1]$. However, the sum of two concave functions is also concave and so the result follows.
\end{proof}
